---
title: "unique-candidates-list"
output: html_document
date: "2022-10-05"
---

# Install libraries
```{r}
install.packages("tidyverse")
install.packages("dplyr")
library(tidyverse)
library(dplyr)
```

# Import datasets
```{r}
candidates <- read_csv("./Candidate_Listing_2022.csv")
```

# Filtering nc_voters for soley Hispanic or latino candidates and filtering candidates database for solely Nov.8 election
```{r}
rdate_candidates <- filter(candidates, election_dt == "11/08/2022")
rm(candidates)
```

# Create a new column in each dataset, rdate_candidates and HL_ncvoter, called full_name which joins columns: first_name + middle_name + last_name
```{r}
rdate_candidates$full_name = paste(rdate_candidates$first_name, rdate_candidates$middle_name,sep=" ")
rdate_candidates$full_name = paste(rdate_candidates$full_name, rdate_candidates$last_name,sep=" ")
```

# First option to remove unique candidates: By duplicate full_name
```{r}
norep_candidates_st <- rdate_candidates[!duplicated(rdate_candidates$full_name), ]
```

# Second option to remove unique candidates: By removing county_name column and using distinct() function
```{r}
rm_county <- rdate_candidates[,-2]
norep_candidates_nd <- distinct(rm_county)
```

# Export databases
```{r}
write.csv(norep_candidates_st, file = "norep_candidates_st.csv")
write.csv(norep_candidates_nd, file = "norep_candidates_nd.csv")
```

